### 2022-10-12 ersteops/templates/printpdf/rendered_template.tex
fix time to display

    \put(0.37115545,0.5742565){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}X\end{tabular}}}}%

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 77\end{tabular}}}}%

@@

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Masculino\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 12\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%

@@

    \put(0.0271255,0.07062683){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 19:01 \end{tabular}}}}%
    \put(0.05802029,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 100\end{tabular}}}}%
    \put(0.13098371,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 120\end{tabular}}}}%
    \put(0.20988188,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 129/40\end{tabular}}}}%
    \put(0.26601422,0.07073227){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 24\end{tabular}}}}%
    \put(0.32533826,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 98\end{tabular}}}}%
    \put(0.39526948,0.07106162){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 90\end{tabular}}}}%
    \put(0.4490251,0.07053194){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny 6\end{tabular}} }}%

    %Signos Vitales 2

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize sdffsdf\end{tabular}}}}%

      \put(0.79939617,0.25975509){\includegraphics[scale=0.3]{signature_medic}}%
      %\put(0.78960956,0.44450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont Firma Médico\end{tabular}}}}%

    \put(0.58960956,0.11450476){\includegraphics[scale=0.5]{client_signature}}%
    \put(0.64203741,0.04450476){\includegraphics[scale=0.5]{client_signature}}%
    %\put((0.64203741,0.06450476){\includegraphics[scale=0.5]{client_signature}}%
    \put(.64090291,0.20857036){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    %\put(0.64203741,0.06450476){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont NA\end{tabular}}}}%

>>>>

      \put(0.37115545,0.574256){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize X\end{tabular}}}}%

    %Folio
    \put(0.41796551,0.60954148){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 78\end{tabular}}}}%

@@

    %Paciente
    \put(0.08748365,0.54597578){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\tiny F55 - Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.32347436,0.544854){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 5556782349\end{tabular}}}}%
    \put(0.05306258,0.51467754){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.12394486,0.51552412){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize 0\end{tabular}}}}%
    \put(0.11025071,0.53602224){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Lillia Sanchez Jaime\end{tabular}}}}%
    \put(0.11717691,0.52661865){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%

@@

@@

    %Finalizacion
    \put(0.56613143,0.28790386){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%\
    \put(0.59939617,0.27975509){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize NA\end{tabular}}}}%
    \put(0.61896758,0.26988471){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Dr.Chapatin\end{tabular}}}}%
    \put(0.59042647,0.26068666){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize XXX-XXXX-XXX\end{tabular}}}}%
    \put(0.53599859,0.25148177){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize Cacharpo\end{tabular}}}}%
    \put(0.81652804,0.25194696){\color[rgb]{0.11764706,0.20784314,0.36862745}\makebox(0,0)[lt]{\lineheight{1.25}\smash{\begin{tabular}[t]{l}\fontfamily{lmss}\selectfont\scriptsize El Operador\end{tabular}}}}%
